---
title: "LR"
output: html_document
author: "Orla Doyle - PA Team, London"
---
Set up packages. 
```{r}
library(tidyverse)
library(mlr)
library(parallel)
library(parallelMap)
library(ggplot2)
library(palabmod)
```

Set up paths and load the data and var_config file. 
```{r}
path = "F:/orla/HCV_manuscript/"
source(file.path(path, "02_code/utils.R"))
data_tr <- readRDS(file.path(path, "01_data/gilead_train_pos_neg.rds"))
var_config <- read_csv(file.path(path, "01_data/meta_data/hcv_varconfig_counts_freq.csv"))
```

Set up matching, pull ids and variables that should go forward for modelling. 
```{r}
data_tr$test_patient_id[data_tr$label==1] <- data_tr$Patient_Id[data_tr$label==1]
matches <- as.factor(data_tr$test_patient_id)
ids <- utils_get_ids(data_tr, var_config)
data_tr <- utils_get_variables(data_tr, var_config, categorical = TRUE)
data_tr$label <- as.factor(data_tr$label)
```

#Missing data
Set missing values to zero. 
```{r}
# vars = c("COUNT_OF_TX_FOR_MISDIAGNOSIS_COMORBIDITIES_SYMPTOMS_RISK_FACTORS",
#  "CLAIM_COUNT_OF_TX_FOR_MISDIAGNOSIS_COMORBIDITIES_SYMPTOMS_RISK_FACTORS",
#  "COUNT_OF_TX_PROC_FOR_MISDIAGNOSIS_COMORBIDITIES_SYMPTOMS_RISK_FACTORS",
#  "CLAIM_COUNT_OF_TX_PROC_FOR_MISDIAGNOSIS_COMORBIDITIES_SYMPTOMS_RISK_FACTORS")
# data_tmp = data_tr[, vars]
# data_tmp[is.na(data_tmp)] = 0
# data_tr[, vars] = data_tmp

data_tr[is.na(data_tr)] <- 0

```

Define MLR compatible dataset. 
```{r}
target = "label"
dataset_tr <- makeClassifTask(id="hcv", data=data_tr, target=target, 
                              positive=1, blocking=matches)

```

Define the learner and fit it to the training data. 
```{r}
lr <- makeLearner("classif.logreg", predict.type = "prob", predict.threshold = 0.5)
lr.fit <- train(lr, dataset_tr)
saveRDS(lr.fit, file.path(path,"03_results/LR/LR_HCV_counts_freq_1_50.rds"))
```
Load first set of hold out data and set up matching variable and selection modelling variables. 
```{r}
data_ts <- readRDS(file.path(path, "01_data/gilead_holdout1_pos_neg.rds"))
ts_matches <- as.factor(data_ts$test_patient_id)
#ids <- utils_get_ids(data_ts, var_config)
data_ts <- utils_get_variables(data_ts, var_config, categorical = TRUE)
data_ts$label <- as.factor(data_ts$label)
```
Make MLR data object from test data. 
```{r}
dataset_ts <- makeClassifTask(id="hcv_ts", data=data_ts, target="label",
                                 positive=1, blocking=ts_matches)
```
Apply the model to the test data. 
```{r}
pred_ts <- predict(lr.fit, dataset_ts)
pr_grpl <- perf_binned_perf_curve(pred_ts, 20,"rec", "prec")
plot(pr_grpl$curve$rec_binned, pr_grpl$curve$prec)
write.csv(pr_grpl$curve, file.path(path,"03_results/LR/PR_LR_HCV_counts_freq_1_50.rds"))
```
Extract the coefficients of the LR model. 
```{r}
lr.coef <-  as.data.frame(lr.fit$learner.model$coefficients)
write.csv(lr.coef, paste0(path, "03_results/LR/coef_LR_HCV_counts_freq_1_50.csv"))
```

Apply model only to treated test cases. 
```{r}
# data_ts <- readRDS(file.path(path, "01_data/gilead_holdout1_pos_neg.rds"))
# pos_ts_tx <- data_ts[data_ts$TREAT_FOR_HCV == 1,]
# data_ts_tx <- data_ts  %>% filter(test_patient_id %in% pos_ts_tx$Patient_Id)
# 
# ts_tx_matches <- as.factor(data_ts_tx$test_patient_id)
# #ids <- utils_get_ids(data_ts, var_config)
# data_ts_tx <- utils_get_variables(data_ts_tx, var_config, categorical = TRUE)
# data_ts_tx$label <- as.factor(data_ts_tx$label)
# dataset_ts_tx <- makeClassifTask(id="hcv_ts", data=data_ts_tx, target="label",
#                                  positive=1, blocking=ts_tx_matches)
# pred_ts_tx <- predict(lr.fit, dataset_ts_tx)
# pr_grpl_tx <- perf_binned_perf_curve(pred_ts_tx, 20,"rec", "prec")
# plot(pr_grpl_tx$curve$rec_binned, pr_grpl_tx$curve$prec)
```